---
title: "K&S_Table1"
output: html_notebook
---

This file translate the state code in the file `create_complete_data1.do` provided by the authors

Specify location files

```{r}
homeDir = "/Users/rw/Documents/Replication/Knight_Schiff/Knight_Schiff_2010"
dataDir = file.path(homeDir,"Data")
inputDir = file.path(dataDir, "Input")
outputDir = file.path(dataDir, "Output")
plotsDir = file.path(homeDir, "Plots")
codeDir = file.path(homeDir, "Code")
```

Load libraries here
```{r}
library(foreign)
library(dplyr)
library(haven)
```

Load the datasets
```{r}
primaries = read_dta(file.path(inputDir,"primaries.dta"))
data2004nationalrolling4 = read_dta(file.path(inputDir,"data2004nationalrolling4.dta"))
data2004nhcross3 = read_dta(file.path(inputDir,"data2004nhcross3.dta"))
dem_aggregate_cnn2v9 = read_dta(file.path(inputDir,"2004_dem_aggregate_cnn2v9.dta"))
state_dists_miles_wide = read_dta(file.path(inputDir,"state_dists_miles_wide.dta"))
```

Merge `dem_aggregate_cnn2v9.dta` with `state_dists_miles_wide` on the variable `cnt`. Keep the variables `toma` `tonc` `toar` and `tovt`. 


Collate the names and variable labels

```{r}
#vars <- data.frame("name" = names(data), "label" = sapply(data, function(x) attr(x, "label")) %>% as.character(), "labelled" = sapply(data, is.labelled) )

#names(data) <- vars$label
```


```{r}
merged1 = full_join(dem_aggregate_cnn2v9, state_dists_miles_wide, by="cst")
merged1 = merged1 %>% select(c(colnames(dem_aggregate_cnn2v9),"toma", "tonc", "toar", "tovt"))
merged1 = merged1 %>% filter(!is.na(t))
```

Replace `wd` and `nb` codes with `NA`
```{r}
merged1$edwards = as.numeric(merged1$edwards)
merged1$clark = as.numeric(merged1$clark)
merged1$lieberman = as.numeric(merged1$lieberman)
merged1$sharpton = as.numeric(merged1$sharpton)
merged1$dean = as.numeric(merged1$dean)
```

Generate the logarithm of the ratio of votes for `dean` over `kerry` and similarly for `edwards`. 

```{r}
merged1$ldean = log(merged1$dean/merged1$kerry)
merged1$ledwards = log(merged1$edwards/merged1$kerry)
```

Rename `nt` as `nt_old`

```{r}
merged1 = rename(merged1, nt_old = nt)
```

Create a new variable `nt` that counts by `t`

```{r}
tally_d = merged1 %>% group_by(t) %>% tally()
tally_d = rename(tally_d, nt = n)
```

Merge this into the previous dataset and name this dataset `complete_data1.dta`. 

```{r}
complete_data1 = full_join(merged1, tally_d, by="t")
```

Take the mean of each of the following variable by `t`: `ldean`, `ledward`, `nt`, `tovt`, 
`toma` and `tonc`. 

```{r}
summary1 = complete_data1 %>% 
  group_by(t) %>% 
  summarise(across(c(ldean,ledwards,nt,tovt,toma,tonc),~mean(.x,na.rm=TRUE)))
```

Generate the relative distances to Vermont and North Carolina

```{r}
summary1$reltovt = summary1$tovt - summary1$toma
summary1$reltonc = summary1$tonc - summary1$toma
```

Rename the variable `nt` to `n`

```{r}
summary1 = rename(summary1, n = nt)
```


